---
title: "Exercise 1"
author: "Saurabh Mishra"
date: "11 February 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 16

We have asked the age of a group of 12 students. While 10 of them provided us with this information, 2 of them did not. We have constructed the vector age that captures this information.
If we were interested in getting the vector without the missing values, which of the following lines of code would be useful to achieve this purpose?(Select all that apply)

```{r}
age <- c(12, 28, 35, 27, NA, 25, 32, 45, 31, 23, NA, 34)

age[-c(5, 11)]
age[c(-5, -11)]
age[c(1, 2, 3, 4, 6, 7, 8, 9, 10, 12)]
age[!is.na(age)] 

x <- list(values=sin(1:3), ids=letters[1:3], sub=list(foo=42,bar=13))
print(x)
```


### Question 18

Download the data "CitesforSara.csv" into RStudio. This dataset includes paper-level citations from 1969 to 1998. First, read the CSV file into R

```{r}
library(tidyverse)
papers <- read.csv("CitesforSara.csv")
papers_select <- select(papers, journal, year, cites, title, au1)
head(papers_select)

# Let’s take a look at some of the most popular papers. Using the filter() method, how many records exist where there are greater than or equal to 100 citations?

papers %>% filter(cites >= 100) %>% select(title)

# Use the group_by() function to group papers by journal. How many total citations exist for the journal “Econometrica”?

papers %>% group_by(journal) %>% filter(journal == "Econometrica") %>% count(cites)

papers
```


### Question 22

```{r}
library(tidyverse)

papers_female <- select(papers, contains("female"))
papers_female
```

